Fast gravitational wave parameter estimation without compromises

### 2023-02-06 src/tex/ms.tex
Add GW150914 and GW170817 minimum frequency to table 1 caption
Add sentence about calibration and PSD estimation

\begin{table}[hbt!]
    \begin{center}
    \begin{tabular}{ l l l}
    \hline
    \hline
    Parameter & GW150914 & GW170817\\
    \hline
        $M_c$ & $\textbf{0.0171}$ & $\textbf{0.0166}$ \\
        $q$ & $0.0036$ & $0.0004$ \\
        $\chi_1$ & $0.0023$ & $0.0006$ \\
        $\chi_2$ & $0.0098$ & $0.0004$ \\
        $d_L$ & $0.0009$ & $0.0076$ \\
        $\phi_c$ & $0.0003$ & $0.0024$ \\
        $\iota$ & $0.0026$ & $0.0045$ \\
        $\psi$ & $0.0005$ & $0.0034$ \\
        $\alpha$ & $0.0007$ & $0.0242$ \\
        $\delta$ & $0.0020$ & $0.0017$ \\
    \hline
    \hline
    \end{tabular}
    \caption{JSD values for the marginalized distribution of each parameter for
    GW150914 and GW170817 between our code and \textsc{Bilby}. The bold values
    indicate the parameters with the largest JSD.}
    \label{tab:JSD}
    \end{center}
\end{table}

@@

% More features such as marginalization
Furthermore, our current implementation is minimal and we do not make use of
most standard ``tricks'' to accelerate sampling.  In particular, we do not
incorporate (semi)analytic marginalization schemes over parameters such as
time, phase, and calibration parameters \cite{2019PASA...36...10T}. Because of
the already reasonable performance of our sampler thanks to hardware
accelerators, time and phase marginalization is not crucial, as the performance
of our implementation is not significantly impacted by having two extra
dimensions. Nevertheless, having fewer parameters cannot hurt in the future, so
we are looking into incorporating analytic marginalization schemes in our code
as well.

>>>>

\begin{table}[hbt!]
    \begin{center}
    \begin{tabular}{ l l l}
    \hline
    \hline
    Parameter & GW150914 & GW170817\\
    \hline
        $M_c$ & $\textbf{0.0171}$ & $\textbf{0.0166}$ \\
        $q$ & $0.0036$ & $0.0004$ \\
        $\chi_1$ & $0.0023$ & $0.0006$ \\
        $\chi_2$ & $0.0098$ & $0.0004$ \\
        $d_L$ & $0.0009$ & $0.0076$ \\
        $\phi_c$ & $0.0003$ & $0.0024$ \\
        $\iota$ & $0.0026$ & $0.0045$ \\
        $\psi$ & $0.0005$ & $0.0034$ \\
        $\alpha$ & $0.0007$ & $0.0242$ \\
        $\delta$ & $0.0020$ & $0.0017$ \\
    \hline
    \hline
    \end{tabular}
    \caption{JSD values for the marginalized distribution of each parameter for
    GW150914 and GW170817 between our code and \textsc{Bilby}. The bold values
    indicate the parameters with the largest JSD. The minimum frequency used for
    analyzing GW150914 and GW170817 are $20 \rm{Hz}$ and $23 \rm{Hz}$,
    respectively.}
    \label{tab:JSD}
    \end{center}
\end{table}

@@

% More features such as marginalization
Furthermore, our current implementation is minimal and we do not make use of
most standard ``tricks'' to accelerate sampling.  In particular, we do not
incorporate (semi)analytic marginalization schemes over parameters such as time
and phase\cite{2019PASA...36...10T}. Because of the already reasonable
performance of our sampler thanks to hardware accelerators, time and phase
marginalization are not crucial, as the performance of our implementation is not
significantly impacted by having two extra dimensions. We also do not include
calibration uncertainties in this study because of simplicity reason. On top of that, since we are planning
to deploy this pipeline to near online PE, we also need to consider estimating
the PSD on the same timescale, which \cite{Cornish:2021wxy} have proposed
a solution for. We are looking into incorporating analytic marginalization
schemes, calibration uncertainties, and real-time PSD estimation in our code as
well.
